---
title: "Results one-stage MASEM with moderator"
output: word_document
params:
  lavmodel: NA
  REtype: NA
  intervals: NA
  transform: NA
  startv: NA
  moderator: NA
  sumstatmod: NA
  kpercor: NA
  npercor: NA
  ossemfit: NA
  sumfit: NA
  fit: NA
  Sres: NA
  varcorr: NA
  testout: NA
  modsumind: NA
  modsum: NA
  modR2: NA
---

This report contains the output of your one-stage MASEM analysis using webMASEM. 


# Number of studies per correlation coefficient

```{r echo=FALSE}
params$kpercor

```

# Total sample size per correlation coefficient

```{r echo=FALSE}
params$npercor

```

# Output overall analysis

`r params$fit`

```{r echo=FALSE}
plot(params$ossemfit, color = "white")
params$sumfit
params$Sres
params$varcorr

```


# Moderator analysis

The following variable was selected as the moderator: `r params$moderator`

## Summary statistics of moderator

```{r echo = FALSE}
params$sumstatmod
```

## Omnibus test of moderating effects

```{r echo = FALSE}
params$testout
```

## Test of individual moderating effects

```{r echo = FALSE}
params$modsumind
```

## Summary output moderator analysis

```{r echo = FALSE}
params$modsum
```

## Between-studies variances of model-implied correlation coefficients

```{r echo = FALSE}
params$modR2
```


The following function arguments were used in the analysis:

- Random effects type: `r params$REtype`
- Interval type: `r params$intervals`
- Transformation on between-study variances: `r params$transform`
- Start values of between-study variances: `r params$startv`
